---
title: "CA 4 Part B - Linear Regression Analysis"
subtitle: "Analysis of linear regression performed on ramdomly sampled data from a pair of columns from a survey of gamer preferences. This includes statement and testing of assumptions followed by intrepretation and dicussion of obtained results."
author: "Gareth Burger"
date: "January, 2023"
output: 
  html_document:
    code_folding: hide
---

- Attempting to determine whether any two variables are correlated

# Statement of Assumptions
(clearly state any assumptions made with respect to the variables chosen for analysis)

 - the observations are independent i.e. respondents 1 giving their results didn't affects respondent 2's results
 - the values within a particular field, the data is normally distributed
 - homoscedasticity (the data points don't diverge from the linear line, does the data fit within the top and bottom bounding lines)
 - can assume randomly sampled and that no hidden relationships exist (as stated in CA, can restate)
 



# Testing of Assumptions
(provide measures, plots and/or justification for your assumptions)
 - tests for normality - shapiro wilk test
 - test for homoscedasticity
 https://www.scribbr.com/statistics/simple-linear-regression/
 
 

# Results
5. Discuss and interpret the analysis conducted and results obtained.
- degree of correlation, r2 value
- should end with a plot of data and a line that fits the data - use ggplot https://www.youtube.com/watch?v=HPJn1CMvtmI&ab_channel=RProgramming101
# simple package 'include' library and a single call to a single function to make ggplot graph


# R Code
• A 1-3 line description of each R code chunk

```{r Load Data, echo=TRUE}
# R code chunk to load and randomly sample data
# description: to randomly sample the data and to allow some degree of variability across results
# The sample() function in R allows you to take a random sample of elements from a dataset or a vector, either with or without replacement

# load data from the csv
file_name = "./data/amalgamated_game_survey_250_2022.csv"
game_survey_data <- read.csv(file_name)

# sample 200 random elements from the data

# set.seed(some random number) to ensure that we get the same sample each time
set.seed(387)

# sample a random vector of 200 elements from all 250 rows in the game_survey_data dataset
sample_rows <- sample(1:nrow(game_survey_data), 200)
sample_rows

# select the 200 rows that match the sampled row numbers
sample <- game_survey_data[sample_rows, ]
sample
```

Step 3
Look at the data and determine whether it is suitable for linear regression
4 qualities, listed in slides between pages 1-95
https://www.scribbr.com/statistics/simple-linear-regression/

- How well the two data points fit along a line
- Pick two attributes, two columns and determine the degree of correlation between the two variables
- and give some brief discussion and analysis of the correlation
- what is the degree of correlation, are they positively or negatively correlated

```{r}
# R code code calculating linear regression for data

```

```{r}
# R code chunk using GGPLOT2 to generate linear regression plot(s)

```